Monte Carlo as Approximate Polynomial Preconditioning within MCSA

### 2014-05-14 doc/polynomial_note/polynomial.tex
Updating GMRES polynomial figures and discussion.

In our experience, the selection of the preferred method is less clear
cut.  Figure~\ref{fig:gmres_poly} shows the GMRES polynomial with coefficients

@@

two least square solutions is now evident.  All methods perform fairly
well for $m=15$, although the normal equations approach is noticably
larger over portions of the domain.  Finally, for $m=20$ the
eigenvalue-based approach appears the best with the least squares QR
now appearing to suffer.  Table~\ref{tab:gmres_poly} shows the value

@@

of these cases.  Although the eigenvalue-based approach
appears to perform worse at small polynomial orders, it actually
produces the smallest spectral radius for all four cases and is the
only approach to produce a spectral radius that is monotonically decreasing
with polynomial order.
The dramatic variability in the different methods for computing the

@@

\begin{table}
\centering
\caption{Spectral Radius of $\left( \bI - p_m(\bA) \bA \right)$.}
\label{tab:gmres_poly}
\begin{tabular}{ccccc}
\toprule
& \multicolumn{4}{c}{Polynomial Order} \\
\cmidrule(r){2-5}
Method & 5 & 10 & 15 & 20 \\
\midrule
Hessenberg Eigenvalues     & 0.569 & 0.231 & 0.109 & 0.088 \\
Least Squares Normal Eqns. & 0.632 & 0.259 & 0.184 & 0.247 \\
Least Squares QR           & 0.632 & 0.273 & 0.176 & 0.586 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

Our experience, however, differs from this result.
Figure~\ref{fig:gmres_poly} shows the GMRES polynomial with coefficients

@@

two least square solutions is now evident.
For orders $15$ and $20$, however, both the eigenvalue-based approach
and the least squares QR perform very well while the normal equations
solution begins to rapidly degrade.
Table~\ref{tab:gmres_poly} shows the value

@@

of these cases.  Both the eigenvalue approach and the least squares QR
produce monotonically decreasing spectral radii whereas the spectral
radius produced by the normal equations increases at high polynomial
orders.  The least squares QR method seems to produce the most consistent
behavior over the full range of polynomial orders.
The significant variability in the different methods for computing the

@@

\begin{table}
\centering
\caption{Spectral Radius of $\left( \bI - p_m(\bA) \bA \right)$.}
\label{tab:gmres_poly}
\begin{tabular}{ccccc}
\toprule
& \multicolumn{4}{c}{Polynomial Order} \\
\cmidrule(r){2-5}
Method & 5 & 10 & 15 & 20 \\
\midrule
Hessenberg Eigenvalues     & 1.027 & 0.630 & 0.081 & 0.034 \\
Least Squares Normal Eqns. & 0.686 & 0.268 & 0.162 & 0.575 \\
Least Squares QR           & 0.686 & 0.281 & 0.085 & 0.033 \\
\bottomrule
\end{tabular}
\end{table}
